The \dealii{} Library, Version 9.2

### 2020-06-01 9.2/paper.tex
Be more verbose on hp interface.

The interface is now as simple to use as the one for $h$-adaptive mesh refinement.
Consider the following (incomplete) listing as an example: We estimate both error and
smoothness of the finite element approximation. Further, we flag certain fractions of
cells with the highest and lowest errors for refinement and coarsening, respectively
(here: 30\%/3\%). From those cells listed for adaptation, we designate a subset
for $h$- and $p$-adaptation (here: 10\%/90\%).
\todo[inline]{Timo asks: is this a typo in the code where you say 0.9, 0.9?}
The parameters of the corresponding
\texttt{hp::Refinement} function specify the fraction of cells to be $p$-adapted from
those subsets flagged for refinement and coarsening, respectively.
\begin{c++}
Vector<float> estimated_error_per_cell(n_active_cells);
KellyErrorEstimator::estimate(
dof_handler, ..., solution, estimated_error_per_cell, ...);
GridRefinement::refine_and_coarsen_fixed_number(
triangulation, estimated_error_per_cell, 0.3, 0.03);

Vector<float> estimated_smoothness_per_cell(n_active_cells);
SmoothnessEstimator::Legendre::coefficient_decay(
..., dof_handler, solution, estimated_smoothness_per_cell);
hp::Refinement::p_adaptivity_fixed_number(
dof_handler, estimated_smoothness_per_cell, 0.9, 0.9);
hp::Refinement::choose_p_over_h(dof_handler);

>>>>

The interface is now as simple to use as the one for $h$-adaptive mesh refinement.
Consider the following (incomplete) listing as an example: We estimate both error and
smoothness of the finite element approximation. Further, we flag certain fractions of
cells with the highest and lowest errors for refinement and coarsening, respectively
(here: 30\%/3\%). From those cells listed for adaptation, we designate a subset
for $h$- and $p$-adaptation. The parameters of the corresponding
\texttt{hp::Refinement} function specify the fraction of cells to be $p$-adapted from
those subsets flagged for refinement and coarsening, respectively (here: 90\%/80\%),
while the remaining fraction will be $h$-adapted (here: 10\%/20\%).
\begin{c++}
Vector<float> estimated_error_per_cell(n_active_cells);
KellyErrorEstimator::estimate(
dof_handler, ..., solution, estimated_error_per_cell, ...);
GridRefinement::refine_and_coarsen_fixed_number(
triangulation, estimated_error_per_cell, 0.3, 0.03);

Vector<float> estimated_smoothness_per_cell(n_active_cells);
SmoothnessEstimator::Legendre::coefficient_decay(
..., dof_handler, solution, estimated_smoothness_per_cell);
hp::Refinement::p_adaptivity_fixed_number(
dof_handler, estimated_smoothness_per_cell, 0.9, 0.8);
hp::Refinement::choose_p_over_h(dof_handler);
